---
output:
  pdf_document: default
  html_document: default
---
### 1) Simulate data
```{r}
new_drug = rnorm(50, mean = 120, sd = 10)
standard = rnorm(50, mean = 125, sd = 12)
```
### 2) Plot histograms
```{r}
library(ggplot2)
data = data.frame(
  BloodPressure = c(new_drug, standard),
  Group = factor(rep(c("New Drug", "Standard Treatment"), each = 50))
)
ggplot(
  data, 
  aes(x = BloodPressure, fill = Group)
) + geom_histogram(alpha = .75, position = "identity", bins = 15
) + labs(title = "New Drug & Standard Treatment", x = "Blood Pressure", y = "Count"
)
```

### 3) T-test
```{r}
t_test_result = t.test(new_drug, standard)
print(t_test_result)
```

### P value Interpretation: The p value is used to determine significance of a result. The usual significance level it must meet is 0.05, though it is heavily context dependent. In our case the p value was greater than 0.05. Assuming that 0.05 is a good significance level in this context, we CANNOT conclude that the new drug is more effective in reducing blood pressure compared with the standard treatment.  